\LARGE \bf Eye-Tracking: a New Look at Human-Robot Interaction Assessment

### 2014-10-02 paper.tex
Added missing fixme package
update abstract

@@

Eye tracking provides unprecedented access to the users' attention and
engagement during interactive scenarios. Previous research\fixme{refs} has shown
that gaze data can be used as a proxy to understand the underlying
socio-cognitive aspects in not only human-computer interaction but in
human-human interaction as well. In the present decade, off the shelf
eye-trackers have become readily available to the researchers to assess
the users' attention and engagement.

>>>>

\usepackage[draft,footnote,nomargin]{fixme}

@@

Eye tracking provides unprecedented access to the users' attention and
engagement during interactive scenarios. Previous research \cite{hasse2012measure,tien2010measuring,jermann2010using,sharma2012gaze} has shown
that gaze data can be used as a proxy to understand the underlying
socio-cognitive aspects in not only human-computer interaction but in
human-human interaction as well. In the present decade, off the shelf
eye-trackers have become readily available to the researchers to assess
the users' attention and engagement.
